---
title: "Reciprocal Transplants (ITS2)"
author: "Annabel Hughes"
date: "8/18/2022"
output: html_document
---

```{r setup, include=FALSE}
## Knit standards
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, options(knitr.kable.NA = ''))
options(warn = -1)
```

```{r install packages, eval = FALSE, include = FALSE}
#setwd("/Users/annabelhughes/Desktop/Davies\ Lab/Git/Reciprocal_Transplants")
## install phyloseq packages
install.packages("Biostrings")
if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install(version = "3.16") # changed to "3.16" on Colleen's computer to be able to run with R 4.2 (Annabel used "3.14")
BiocManager::install("phyloseq")

```

```{r load packages, echo = FALSE}
#library(dada2) # I have version 1.18.0 downloaded on the SCC for this
library(tidyverse)
library(phyloseq)
library(RColorBrewer)
library(janitor)
library(ggplot2)
library(Rmisc) 
library(RColorBrewer)
library(cowplot)
```

# **ITS2 Assessment** {.tabset}

```{r cleaning up its2 file, eval=TRUE, include=FALSE}
df <- read.table("Data/219_20220803T065042_DBV_20220803T143825.profiles.absolute.abund_and_meta.txt", sep = "\t")[c(-1:-6,-37, -38),-1] %>%
  row_to_names(row_number = 1)
names(df)[1] <- "sampleID"
write.csv(df, "Data/ITS2_symportal_RT.csv", row.names = FALSE)
```

```{r read in ITS2 data}
## read in ITS2 data
its_df <- read.csv("Data/ITS2_symportal_RT.csv") %>% 
  column_to_rownames("sampleID") # making first column of sample IDs the rownames
## read in the meta data from the samples
meta <- read.csv("Data/RT_SSID_microPrep_ITS2_meta.csv") %>% 
  column_to_rownames("Well_ID") %>% # making first column of well IDs the rownames
  mutate(Source = fct_relevel(Source, c('NS', 'BR', 'FR')),
         Transplant = fct_relevel(Transplant, c('NS', 'BR', 'FR')))
```

```{r its2 phyloseq object}
## Make taxa table for phyloseq
taxa_its <- data.frame(colnames(its_df))# extract symb strain data as dataframe
colnames(taxa_its) <- "DIV" # changing the column name to be 'DIV'
taxa_its[2] <- taxa_its %>% separate(DIV, "majority_its2") # create a column for major ITS2 (first part of DIV name)
taxa_its$genus <- str_sub(taxa_its$DIV, 1, 1) # make genus column of symb genus (first letter of DIV)
taxa_its <- taxa_its %>% mutate_if(is.character, as.factor) # convert all columns to factors
rownames(taxa_its) <- taxa_its$DIV # rename rows with DIV ids
taxa_its_matrix <- as.matrix(taxa_its) # convert to a matrix
 
## Create ITS2 taxa phyloseq object 
phylo_its2 <- phyloseq(sample_data(meta),
                       otu_table(its_df, taxa_are_rows = FALSE),
                       tax_table(taxa_its_matrix))
# phylo_its2 # just a sanity to check that we have 5 taxa and 29 samples -- Looks good!
```

### Abundance by individual

```{r calc rel abund and save phylo objc, fig.height = 4, fig.width = 6, fig.align = "center"}

## Calculate relative abundance per sample
phylo_its2_rel <- transform_sample_counts(phylo_its2, function(OTU) OTU/sum(OTU))

## plot relative majority ITS2 by treatment
major_plot <- plot_bar(phylo_its2_rel, x = "Sample_ID", fill = "majority_its2")+
  theme_bw() +
  facet_wrap(~ Source, scales = "free_x") +
  theme(panel.grid = element_blank(), legend.position = "bottom", strip.background = element_blank(), strip.text = element_text(face = "bold"), legend.title = element_blank()) +
  labs(x = "Coral ID", y = "Relative abundance") +
  scale_color_manual(values = c("#252525", "#636363", "#969696", "#cccccc")) +
  scale_fill_manual(values = c("#252525", "#636363", "#969696", "#cccccc")) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 1.02))
#ggsave("Figures/Supplemental_Figures/FigureS9_ITS2.png", height = 4, width = 8, dpi = 600)
#ggsave("Figures/Supplemental_Figures/FigureS9_ITS2.pdf", height = 4, width = 8, useDingbats = FALSE)
## Save both the absolute and relative abundance phyloseq objects
#save(phylo_its2, phylo_its2_rel, file = "Data/ITS2_data/its_phylo_abund.Rdata")
```

**Figure S9.** Relative abundance of major ITS2 types within each coral colony grouped by source location. Light grey represents *Cladocopium goreaui* (C1), which was the dominant ITS2 for all colonies.

```{r}
## stats
its_df_total <- cbind(its_df, total = rowSums(its_df)) #create a new column summing up counts for each sample
mean(its_df_total$total) #mean
sd(its_df_total$total) #standard deviation
min(its_df_total$total) #minimum counts
max(its_df_total$total) #max
```



### Making a new figure after reviewer comments: "Figure S9 - It would be valuable for readers to also have the stacked bar plot of sequences from the raw data, not just the IT2S data. This would reinforce your conclusion that C. goreaui is the primary symbiont in the samples, not just clade C."

```{r cleaning up post-med seqs file, eval=TRUE, include=FALSE}

df_seqs <- read.table("Data/219_20220803T065042_DBV_20220803T143825.seqs.absolute.abund_and_meta.txt", sep = "\t") [c(-31),c(-1,-3:-39)] %>%
  row_to_names(row_number = 1)
names(df_seqs)[1] <- "sampleID"
write.csv(df_seqs, "Data/ITS2_symportal_RT_postmed.csv", row.names = FALSE)

```

```{r read in ITS2 post-med seqs data}

## read in ITS2 data
its_seqs_df <- read.csv("Data/ITS2_symportal_RT_postmed.csv") %>% 
  column_to_rownames("sampleID") # making first column of sample IDs the rownames

```

```{r its2 post-med seqs phyloseq object}

## Make taxa table for phyloseq
taxa_its_seqs <- data.frame(colnames(its_seqs_df))# extract symb strain data as dataframe
colnames(taxa_its_seqs) <- "DIV" # changing the column name to be 'DIV'
#taxa_its_seqs[2] <- taxa_its_seqs %>% separate(DIV, "majority_its2") # create a column for major ITS2 (first part of DIV name)
#taxa_its_seqs$genus <- str_sub(taxa_its_seqs$DIV, 1, 1) # make genus column of symb genus (first letter of DIV)
taxa_its_seqs <- taxa_its_seqs %>% mutate_if(is.character, as.factor) # convert all columns to factors
rownames(taxa_its_seqs) <- taxa_its_seqs$DIV # rename rows with DIV ids
taxa_its_seqs_matrix <- as.matrix(taxa_its_seqs) # convert to a matrix
 
## Create ITS2 seqs phyloseq object 
phylo_its2_seqs <- phyloseq(sample_data(meta),
                       otu_table(its_seqs_df, taxa_are_rows = FALSE),
                       tax_table(taxa_its_seqs_matrix))
# phylo_its2_seqs # just a sanity to check that we have 112 taxa and 29 samples -- Looks good!

```

```{r calc rel abund of seqs and save phylo objc, fig.height = 6, fig.width = 12, fig.align = "center"}

## Calculate relative abundance per sample
phylo_its2_seqs_rel <- transform_sample_counts(phylo_its2_seqs, function(OTU) OTU/sum(OTU))

#generating random color palette
set.seed(6) # setting a seed here to save the colours to randomly generate the same each time
color <- grDevices::colors()[grep('gr(a|e)y', grDevices::colors(), invert = T)]
n <- 112 #number of taxa you have
col <- sample(color, n)
#write.csv(col,"col.csv")
#col_saved <- read.csv("col.csv")[,-1]


## plot relative majority ITS2 by treatment
post_plot <- plot_bar(phylo_its2_seqs_rel, x = "Sample_ID", fill = "DIV") + #Looking at DIV rel abundance
  theme_bw() +
  facet_wrap(~ Source, scales = "free_x") +
  theme(panel.grid = element_blank(), legend.position = "bottom", strip.background = element_blank(), strip.text = element_text(face = "bold"), legend.key.size = unit(0.4, 'cm'), legend.title = element_blank()) +
  scale_fill_manual(values = col) +
  guides(fill = guide_legend(ncol = 10)) +
  labs(x = "Coral ID", y = "Relative abundance") +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 1.02))
#ggsave("FigS9A_ITS2_RT.png", height = 6, width = 15, dpi = 600)
#ggsave("FigS9A_ITS2_RT.pdf", height = 6, width = 15, useDingbats = FALSE)

```

</br>
</br>

# Final Figure S9

```{r final fig S9, fig.align='center', fig.width=10, fig.height=10}

library(patchwork)

## set the layout
layout <- "
AAAA
BBBB
"

## add plots together with layout
major_plot + post_plot + plot_layout(design = layout) + plot_annotation(tag_levels = 'A')

ggsave("Figures/Supplemental_Figures/FigureS9_ITS2.png", height = 10, width = 10, dpi = 800)
ggsave("Figures/Supplemental_Figures/FigureS9_ITS2.pdf", height = 10, width = 10, useDingbats = FALSE)

```

**Figure S9.** Relative abundance of major ITS2 types (A) as well as the post-med sequences (B) within each coral colony grouped by source location. The dominant algal symbiont species was determined to be Cladocopium goreaui (C1) for all collected corals.

</br>

### Session Info:
```{r}

sessionInfo()

```

